---
title: "Getting Started with biostatAnki"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with biostatAnki}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(biostatAnki)
```

## Overview

**biostatAnki** is an Anki-style quiz app for biostatistics in R.
The package ships 60 questions covering descriptive statistics, correlation,
and simple linear regression.
Users write R code to answer each question; the app evaluates the result
against the expected output.

## Installation

```r
# From GitHub (development version)
# install.packages("pak")
pak::pak("jorge-alcantara/biostatAnki")
```

## Browsing the question bank

`load_questions()` returns all 60 questions as a data frame.

```{r load}
qs <- load_questions()
nrow(qs)
names(qs)
```

Each row has three columns:

| Column | Description |
|--------|-------------|
| `id` | Integer question ID (1–60) |
| `question` | The biostatistics prompt |
| `code` | Canonical solution code |
| `expected_output` | Expected result as a character string |

## Fetching a single question

`get_question(id)` returns one question as a list.

```{r get}
q <- get_question(1)
cat(q$question)
```

## Checking an answer

`check_answer(user_code, expected_output)` evaluates `user_code` in a clean
environment and returns `TRUE` when the result matches `expected_output`.

```{r check-correct}
# Correct answer
check_answer(q$code, q$expected_output)
```

```{r check-wrong}
# Wrong answer
check_answer("mean(1:10)", q$expected_output)
```

Numeric comparisons use a tolerance of `1e-6`, so floating-point results work
as expected:

```{r tolerance}
check_answer("0.1 + 0.2", "0.3")  # TRUE despite floating-point representation
```

## Validating the full question bank

`validate_questions()` runs every canonical solution through `check_answer()`
and reports how many pass.

```{r validate}
result <- validate_questions()
cat(sprintf("%d / %d questions pass\n", result$passed, result$total))
```

## Launching the interactive app

The Shiny interface lets you navigate questions, type code, and get instant
feedback:

```r
biostatAnki::run_app()
```

The app opens in your default browser. Use the **Previous / Next** buttons to
navigate and the **Check** button to evaluate your answer.
